---
title: "Shapes of graph and eigen vectors"
output: html_document
---

## Introduction

The shapes should affect on the eigen vectors.

We expect that the symmetricity should strongly affect on the appearance of eigen vectors along with their corresponding eigen values.


## Plans

* Make a simple graph and calculate their eigen vectors.
* Combine/Connect multiple simple graphs and calculate their eigen vectors.
* Attempt to identify relation between eigen vectors and the connection pattern.
* Initially we should start flat grphs, so that we can relatively easily identify the rules if any.
基本形ltticeを作成（座標とグラフオブジェクトとしての情報）


## Strategies

* Generate latties
* Connect lattices
* Eigen-decompose their adj matrices
* Color the graph with eigen vector element values

## Utility functions
```{r setup, include=FALSE}
library(knitr)
library(rgl)
knit_hooks$set(webgl = hook_webgl)
```

```{r}
my.col.st <- function(x,N=5){
  floor((x-min(x))/(max(x)-min(x)) * 0.99 * N)+1
}

my.color.point <- function(X,col,cex=0.5){
  n <- length(unique(col))
  ucol <- unique(col)
  for(i in 1:n){
    tmp <- which(col==ucol[i])
    points(X[tmp,],pch=20,col=ucol[i],cex=cex)
  }
}
my.color.sphere <- function(X,col,radius=1){
  n <- length(unique(col))
  ucol <- unique(col)
  for(i in 1:n){
    tmp <- which(col==ucol[i])
    spheres3d(X[tmp,],color=ucol[i],radius=radius)
  }
}

```

### Lattice in the shape of regtangle
```{r}
my.rect.lattice <- function(xy){
  X <- 0:xy[1]
  Y <- 0:xy[2]
  XY <- as.matrix(expand.grid(X,Y))
  n <- length(XY[,1])
  d <- as.matrix(dist(XY,method="manhattan"))
  adj <- matrix(0,length(d[1,]),length(d[,1]))
  adj[which(d==1)] <- 1
  return(list(X=XY,n=n,adj=adj))
}
xy <- c(50,50)
out <- my.rect.lattice(xy)
plot(out$X,pch=20,cex=0.001)
```

## Connect two squares for example with only one shared vertex

### Two same size squares
```{r}
xy <- c(25,25)
out <- my.rect.lattice(xy)
plot(out$X,pch=20,cex=0.001)
X2 <- rbind(out$X,out$X + 25)
plot(X2)
adj <- matrix(0,out$n*2-1,out$n*2-1)
adj[1:out$n,1:out$n] <- out$adj
adj[out$n:(2*out$n-1),out$n:(2*out$n-1)] <- out$adj
eigen.out <-eigen(adj)
```
```{r}
p <- 1 
col <- my.col.st(eigen.out[[2]][,p],N=5)
plot(X2,pch=20,cex=0.0001)
my.color.point(X2,col,cex=1)
```

Plot series of eigen vectors
```{r}
for(i in 1:20){
  col <- my.col.st(eigen.out[[2]][,i],N=5)
  plot(X2,pch=20,cex=0.0001,main=paste(i, "-st"))
  my.color.point(X2,col,cex=1)
}
```


### Two different size squares
```{r}
xy1 <- c(35,35)
xy2 <- c(15,15)
out1 <- my.rect.lattice(xy1)
out2 <- my.rect.lattice(xy2)
#plot(out$X,pch=20,cex=0.001)
X2 <- rbind(out1$X,out2$X + 35)
#plot(X2)
adj <- matrix(0,out1$n+out2$n-1,out1$n+out2$n-1)
adj[1:out1$n,1:out1$n] <- out1$adj
adj[out1$n:(out1$n+out2$n-1),out1$n:(out1$n+out2$n-1)] <- out2$adj
eigen.out <-eigen(adj)
```
```{r}
p <- 1 
col <- my.col.st(eigen.out[[2]][,p],N=5)
plot(X2,pch=20,cex=0.0001)
my.color.point(X2,col,cex=1)
```

Plot series of eigen vectors
```{r}
for(i in 1:20){
  col <- my.col.st(eigen.out[[2]][,i],N=5)
  plot(X2,pch=20,cex=0.0001,main=paste(i, "-st"))
  my.color.point(X2,col,cex=1)
}
```


### Two same size squares but one square's tip is connected to a point inside of the other square

```{r}
xy <- c(25,25)
out <- my.rect.lattice(xy)
plot(out$X,pch=20,cex=0.001)

adj <- matrix(0,out$n*2-1,out$n*2-1)

adj[out$n:(2*out$n-1),out$n:(2*out$n-1)] <- out$adj
#adj[out$n,out$n] <- 0
s <- sample(1:out$n,1)
ss <- 1:out$n
ss[s] <- out$n
ss[out$n] <- s
adj[ss,ss] <- out$adj
```
```{r}
eigen.out <-eigen(adj)
```
```{r,webgl=TRUE}
X. <- cbind(out$X,rep(0,out$n))
X.[,1] <- X.[,1] - out$X[s,1]
X.[,2] <- X.[,2] - out$X[s,2]

X.. <- cbind(rep(0,out$n),out$X %*% matrix(c(1,-1,1,1)*1/sqrt(2),2,2))
X2 <- rbind(X.,X..)
p <- 1
col <- my.col.st(eigen.out[[2]][,p],N=5)
plot3d(X2) 
my.color.sphere(X2,col)
```

```{r}
p <- 1 
col <- my.col.st(eigen.out[[2]][,p],N=5)
plot(X2,pch=20,cex=0.0001)
my.color.point(X2,col,cex=1)
```

Plot series of eigen vectors
```{r}
for(i in 1:20){
  col <- my.col.st(eigen.out[[2]][,i],N=5)
  plot(X2,pch=20,cex=0.0001,main=paste(i, "-st"))
  my.color.point(X2,col,cex=1)
}
```


### Teo different size squares
```{r}
xy1 <- c(35,35)
xy2 <- c(15,15)
out1 <- my.rect.lattice(xy1)
out2 <- my.rect.lattice(xy2)
#plot(out$X,pch=20,cex=0.001)
X2 <- rbind(out1$X,out2$X + 35)
#plot(X2)
adj <- matrix(0,out1$n+out2$n-1,out1$n+out2$n-1)
adj[1:out1$n,1:out1$n] <- out1$adj
adj[out1$n:(out1$n+out2$n-1),out1$n:(out1$n+out2$n-1)] <- out2$adj
eigen.out <-eigen(adj)
```
```{r}
p <- 1 
col <- my.col.st(eigen.out[[2]][,p],N=5)
plot(X2,pch=20,cex=0.0001)
my.color.point(X2,col,cex=1)
```

Plot series of eigen vectors
```{r}
for(i in 1:20){
  col <- my.col.st(eigen.out[[2]][,i],N=5)
  plot(X2,pch=20,cex=0.0001,main=paste(i, "-st"))
  my.color.point(X2,col,cex=1)
}
```

